\CatchFileBetweenTags{\AlphaInvVal}{constants.tex}{AlphaInvVal}
\CatchFileBetweenTags{\AlphaSVal}{constants.tex}{AlphaSVal}
\CatchFileBetweenTags{\WeakAngleVal}{constants.tex}{WeakAngleVal}
\CatchFileBetweenTags{\HiggsVEVVal}{constants.tex}{HiggsVEVVal}
\CatchFileBetweenTags{\FermiConstVal}{constants.tex}{FermiConstVal}
\CatchFileBetweenTags{\HiggsMassVal}{constants.tex}{HiggsMassVal}
\CatchFileBetweenTags{\ElectronYukawaVal}{constants.tex}{ElectronYukawaVal}
\CatchFileBetweenTags{\JarlskogEq}{constants.tex}{JarlskogEq}
\CatchFileBetweenTags{\JarlskogVal}{constants.tex}{JarlskogVal}
\CatchFileBetweenTags{\CabibboAngleVal}{constants.tex}{CabibboAngleVal}
\CatchFileBetweenTags{\WBosonMassVal}{constants.tex}{WBosonMassVal}
\CatchFileBetweenTags{\CabibboAngleEq}{constants.tex}{CabibboAngleEq}
\CatchFileBetweenTags{\VacuumEnergyScaleVal}{constants.tex}{VacuumEnergyScaleVal}
\CatchFileBetweenTags{\combinedtotalchiVal}{constants.tex}{combinedtotalchiVal}
\CatchFileBetweenTags{\combinedreducedchiVal}{constants.tex}{combinedreducedchiVal}

\begin{abstract}
When a persistent system's internal complexity exceeds the capacity of a single control loop, it must structurally partition or collapse. We introduce three universal rules governing this partitioning: Capacity Partitioning (distributing finite bandwidth across orthogonal demands), Reversible Encoding (conserving non-integer mismatches to avoid Landauer erasure), and Impedance Matching (minimizing reflection loss between nested layers). These rules bridge the gap between architectural requirements (what persistent systems must be) and operational mechanics (how they continue to persist). Because the quantum vacuum is a closed persistent system with no external environment, it provides the most stringent possible test. Applying these rules to the $E_8$ substrate derived in companion works, we show that the constants of the Standard Model and General Relativity emerge as the exact, parameter-free capacity allocations. The kinematic behavior of the Standard Model maps to the thermodynamic limits of a finite-bandwidth network. Gauge couplings arise as bandwidth fractions under Capacity Partitioning (the strong coupling, QCD beta function coefficients, weak mixing angle, Cabibbo angle, and Jarlskog invariant). Electroweak mass scales arise as impedance-matching thresholds under Impedance Matching at the Resonant Interface (the Higgs vacuum expectation value, Fermi constant, W-boson and Higgs masses). Gravitational scales arise as the conserved geometric attenuation of Reversible Encoding across the Geometric Depth (the Planck mass and vacuum energy density), simultaneously resolving the Gravitational Hierarchy and the Vacuum Catastrophe. A zero-degree-of-freedom global geometric fit spanning 64 orders of magnitude ($\alpha^{-1}$, $G_F$, $M_W$, $\alpha_s$, $M_H$, $\sin^2\theta_W$, $\theta_C$, $J$, $M_P$, $R_K$) yields a reduced $\chi^2 \approx 1.05$. This convergence demonstrates that the fundamental constants arise as the structurally necessary partition coefficients of a finite information substrate.
\end{abstract}