\section{The Physics Validation: The \texorpdfstring{$E_8$}{E8} Substrate and the Geometric Cascade}
\label{sec:physics_validation}

As derived in \textit{Informational Energetics: A Universal Architecture of Persistence} \cite{meyer_informational_2026}, the vacuum is the unique resource-constrained computational substrate satisfying the six architectural pillars of persistence: an $E_8$ lattice projected to $D=4$ spacetime, with each localized node possessing strictly finite channel capacity ($\nu = 16$). This substrate contains four key invariants: the temporal resonance $\Delta=43$, the chiral capacity $\nu=16$, the interaction rank $\sigma=5$, and the topological boundary $\chi=2$, all derived from the $E_8 \rightarrow D_4 \oplus D_4$ projection.

While we derived the functional operator forms in \textit{Informational Energetics: Entropic Action} \cite{meyer_ieaction_2026}, the numerical coefficients remained undetermined. Standard QFT treats these constants as independent empirical inputs, each determined by measurement. In the IE framework, they emerge as coupled partition coefficients of a single finite capacity budget. Unlike $\alpha^{-1}$, which represents the unpartitioned baseline impedance derived directly from the substrate, the remaining parameters are not fundamental. They emerge strictly as the partition coefficients of the vacuum's finite channel capacity ($\nu = 16$): the unique allocation required for nested subsystems to satisfy global solvency.

If the spatial geometry, temporal updates, and internal force generators all attempt to saturate the node simultaneously, local complexity exceeds the 16 available channels and the causal structure becomes unresolvable. Because the vacuum persists, its structure must satisfy the three rules of Nested Persistence (\cref{sec:nested_persistence}). The $\nu = 16$ budget is therefore partitioned across orthogonal interaction sectors. We apply the three rules of Nested Persistence sequentially:

\textbf{Capacity Partitioning} allocates the $\nu = 16$ chiral capacity across orthogonal geometric sectors. This yields \textbf{System 4: The Gauge Partition}, whose protocol defines three bandwidth fractions: the saturation ratio (Strong Coupling $\alpha_s$), the spacetime split (Weak Mixing Angle $\sin^2\theta_W$), and the generational leakage rate (Cabibbo Angle $\theta_C$). The irreducible geometric frustration of projecting 5-fold symmetry onto 4-fold spacetime manifests 
as the Jarlskog Invariant $J$. Because the temporal and color sectors are geometrically isolated by this partition, we show that the Strong CP problem is structurally prohibited without requiring an axion.

\textbf{Reversible Encoding} conserves the geometric mismatches that Capacity Partitioning cannot evenly divide. The coordinate origin on the discrete lattice consumes one site from the $D\Delta = 172$ manifold, yielding the Coordinate 
Overhead $\eta = 171/172$. The minimum resolvable topological mismatch is stored as the Electron Yukawa $y_e$, the mass floor below which vacuum fluctuations erase distinguishable states. At the bulk scale, the irreducible attenuation remainder manifests as the Vacuum Energy Density $\rho_{vac}$.

\textbf{Impedance Matching} stabilizes the boundary between the high-frequency vacuum resonance and local topological defects (Matter). This yields \textbf{System 5: The Resonant Interface}, dynamically generating the electroweak mass scale: the Higgs VEV ($v$), Fermi constant, and Electron Yukawa ($y_e$).

\textbf{Capacity Partitioning} again governs the residual bandwidth left after surface allocations, now attenuated across the geometric bulk. This yields \textbf{System 6: The Geometric Depth}, identified as Gravity. Signal attenuation derives the Planck scale ($M_P$) and Cosmological Constant ($\Lambda$), resolving the Gravitational Hierarchy and Vacuum Catastrophe.

\subsection{Note on Absolute Scale}

A discrete lattice inherently produces pure dimensionless ratios (e.g., $v/m_e \approx 4.8 \times 10^5$). To express these in laboratory units, one mass scale must be fixed, just as expressing the speed of light in $\mathrm{m/s}$ requires the definition of a meter. 

In the $E_8$-Persistence theory, the electron mass is not an external input. It is the \textbf{Landauer Limit} of the substrate: the minimum resolvable topological defect, derived below in \cref{subsec:margin_electron} as the Margin output of System 5. Any lighter charged state would possess binding energy below the vacuum's thermal noise floor and dissolve into indistinguishable fluctuations. The electron is the \emph{smallest non-erasable unit of mass}.

We therefore adopt $m_e \approx 0.511\,\mathrm{MeV}$ as the \textbf{natural unit} of the mass spectrum, not a tunable parameter, but the structural floor that the partitioning rules necessarily produce. All higher mass scales ($v$, $M_W$, $M_H$, $M_P$) follow as strict geometric multiples of this floor, with zero additional degrees of freedom. The convention does not enter the derivations; it merely reports the theory's native dimensionless ratios in the units of experimental measurement.

This derivation cascade spans 64 orders of magnitude, from the gravitational coupling ($10^{-45}$) to the Planck mass ($10^{19}$ GeV) with \textbf{zero tunable parameters}. Every mass, angle, and coupling flows strictly from the $E_8$-Persistence theory substrate.