\section{The Capacity Partition (System 4)}
\label{sec:capacity_partition}

As established in \textit{Informational Energetics: A Universal Architecture of Persistence} \cite{meyer_informational_2026}, the vacuum is a resource-constrained computational substrate and each localized node possesses a strictly finite channel capacity ($\nu = 16$). 

This strict hardware limit presents a systemic threat: if the spatial geometry, temporal updates, and internal force generators all attempt to saturate the node simultaneously, local complexity exceeds the 16 available channels and the causal 
structure becomes unresolvable. We term this \textbf{Bandwidth Exhaustion}. The three rules resolve this by the strict partitioning of the $\nu = 16$ budget across orthogonal interaction sectors.

\subsection{The System Specification}

We define the Capacity Partition by instantiating the six architectural pillars of persistence \cite{meyer_informational_2026}. Here they take the following specific forms in the gauge sector:

\begin{enumerate}
    \item \textbf{Capacity: The Chiral Bandwidth ($\nu = 16$).} 
    The vacuum possesses 16 chiral degrees of freedom. This is the absolute processing budget that must be allocated without overflow.
    
    \item \textbf{Map: The Gauge Topology ($\sigma=5, \chi=2$).} 
    The system must map the internal interaction generators (rank $\sigma=5$) and the localized boundaries ($\chi=2$) onto the substrate. These topological invariants define the number of distinct interaction apertures that require bandwidth.
        
    \item \textbf{Protocol: The Geometric Partitions ($\alpha_s, \sin^2\theta_W, \theta_C$).}
    These three dimensionless ratios serve as the mathematically independent partition coefficients of the Standard Model. In standard Quantum Field Theory, the individual gauge couplings ($g_1, g_2, g_3$) are treated as fundamental, independent primitives; here, they are algebraic composites. 
    In this framework, these three dimensionless ratios are the mathematically independent partition coefficients. The individual gauge couplings ($g_1, g_2, g_3$) of standard QFT are algebraic composites of these underlying geometric allocations:

    \begin{itemize}
        \item \textbf{Saturation Ratio} (Strong Coupling $\alpha_s$): The fraction of total chiral bandwidth utilized.
        \item \textbf{Spacetime Partition} (Weak Angle $\sin^2\theta_W$): The split between temporal and spatial bandwidth allocation.
        \item \textbf{Generation Coupling} (Cabibbo Angle $\theta_C$): The controlled leakage rate between generational tiers.
    \end{itemize}
    
    \item \textbf{Governor: Field Rigidity ($\beta_0$).} 
    To prevent high-energy localized perturbations from warping the partition ratios and causing an overflow, the vacuum must possess structural rigidity. The QCD beta function coefficients encode this exact anti-screening resistance to gauge field deformation.
 
    \item \textbf{Toll: Projection Frustration ($J$).} 
    The system cannot perfectly map a 5-fold internal symmetry ($H_4$ icosahedral structure) onto a 4-dimensional spacetime manifold ($D=4$). This irreducible geometric mismatch manifests as the Jarlskog Invariant, the measurable thermodynamic friction of the causal projection, which acts as the physical origin of CP violation.

    \item \textbf{Margin: Minimum Resolvable Impedance ($y_e$).} 
    The partition must maintain a noise floor. The Electron Yukawa coupling represents the smallest non-zero fractional allocation distinguishable from vacuum fluctuations. (The Electron Yukawa sets the absolute baseline for mass generation; its derivation is deferred to \cref{sec:resonant_interface}, where it emerges as the minimum resolvable impedance of the resonant interface.)
\end{enumerate}

\subsection{The Coordinate Overhead (\texorpdfstring{$\eta$}{eta})}

Before the Protocol can assign bandwidth to the individual forces, the Capacity Partitioning rule demands it first pay the structural cost of establishing a coordinate system. In information theory, this is identical to \textbf{Data Framing overhead}. To transmit a packet of $N$ bits, at least one bit must act as the synchronization anchor (the ``start'' bit), leaving $N-1$ bits for the payload. By the \textbf{Fencepost Principle}, $N$ discrete points define exactly $N-1$ addressable intervals.

The $E_8$ substrate's local causal neighborhood possesses a finite Manifold Resolution of $R_M = D \times \Delta = 4 \times 43 = 172$ spacetime addresses per fundamental cycle. On a discrete lattice, permanently defining a coordinate origin consumes exactly one site, leaving $171$ relative, addressable coordinate states. The Coordinate Overhead $\eta$ is therefore the strict ratio of Addressable Capacity to Total Geometric Volume:

\begin{equation}
\label{eq:coordinate_overhead}
\eta \equiv \frac{N_{addressable}}{N_{total}} = \frac{D\Delta - 1}{D\Delta} = 1 - \frac{1}{172} \approx 0.994186
\end{equation}

On a discrete lattice, defining a coordinate system requires selecting an origin. This origin site is 'occupied' by the reference frame itself and cannot simultaneously carry physical state information. The remaining $D\Delta - 1$ sites constitute the addressable capacity. This is identical to data framing in communication protocols: to transmit $N$ bits, one bit must serve as the start-of-frame delimiter.

\textit{Scope Defense:} Note that the temporal resonance ($\Delta = 43$) does not incur this overhead: as a periodic cycle with no endpoints, it requires no origin fixing. The coordinate overhead applies strictly to the spatial manifold volume ($D\Delta = 172$), where a discrete reference frame must be established.

Because the Coordinate Overhead arises from fixing a reference frame within the $D=4$ manifold volume, it applies exclusively to quantities that integrate over this bulk volume (4-forms), such as the channel saturation that determines $\alpha_s$. Quantities defined by boundary topology (1-forms, Wilson Loops, the Euler characteristic $\chi$) do not reference the internal coordinate grid and are therefore geometrically exact; this is why the Fine-Structure Constant ($\alpha^{-1}$) required no such correction. When an operator involves both boundary topology and bulk integration, $\eta$ applies strictly to the volumetric component and not to the topological invariants.

% --- Load Dynamic Nc Tags ---
\CatchFileBetweenTags{\NcVal}{constants.tex}{NcVal}
\CatchFileBetweenTags{\NcEq}{constants.tex}{NcEq}

\subsection{The Interaction Remainder: Geometric Origin of Color Charge (\texorpdfstring{$N_c = 3$}{Nc = 3})}

In the Standard Model, $N_c = 3$ is an empirical input. Its value is determined by the requirement of Anomaly Cancellation: for the electroweak theory to be mathematically consistent, the sum of charges over all fermions in a generation must vanish, which requires exactly three quark colors to offset the leptons.

In the $E_8$-Persistence theory, this is a strict topological necessity. ``Color'' is identified geometrically as the \textbf{Interaction Remainder}. The topological boundary ($\chi = 2$) is a spherical surface that locks two generators to maintain the defect's structural identity against the vacuum, analogous to the two poles required to define a sphere.

To embed a persistent physical particle (a topological knot) into the vacuum, the system must map the lattice's fundamental interaction generators ($\sigma = 5$) onto the topological boundary of the defect ($\chi = 2$). The degrees of freedom not consumed by this boundary lock constitute the active internal bulk available for strong force mediation:

\begin{equation}
    N_c \equiv \NcEq = \mathbf{\NcVal}
\end{equation}

This derives the number of quark colors. The $N_c=3$ requirement for Standard Model anomaly cancellation is identically the geometric surplus required to embed a $\chi=2$ spherical boundary within a $\sigma=5$ interaction manifold. 

Anomaly cancellation in the Standard Model is the algebraic expression of Geometric Flux Conservation in this framework. Information (phase flux) cannot be created or destroyed at a lattice node; the flux entering the 3-dimensional color bulk must perfectly balance the flux traversing the 2-dimensional topological boundary, naturally enforcing the hypercharge assignments of the Standard Model.