\subsection{Jarlskog Invariant \texorpdfstring{$J$}{J}: The Projection Frustration}
\label{subsec:jarlskog}

\CatchFileBetweenTags{\JarlskogVal}{constants.tex}{JarlskogVal}
\CatchFileBetweenTags{\JarlskogExperimentalValue}{constants.tex}{JarlskogExperimentalValue}
\CatchFileBetweenTags{\JarlskogSigma}{constants.tex}{JarlskogSigma}

\subsubsection{The Architectural Requirement}
Under \textbf{Rule 2: Reversible Encoding}, the irreducible geometric mismatch of projecting 5-fold symmetry onto a 4-fold manifold cannot be erased; it must be stored as the measurable thermodynamic friction of the causal projection.

The \textbf{Toll} pillar of the Capacity Partition is the \textbf{Causal Toll}: the irreducible thermodynamic friction of mapping the 5-fold internal symmetry of the lattice ($\sigma=5$) onto the 4-dimensional spacetime manifold ($D=4$). In the Standard Model, this manifests as the Jarlskog Invariant ($J \approx 3 \times 10^{-5}$), which quantifies CP violation but whose magnitude has no structural explanation.

We identify $J$ geometrically as this exact \textbf{Projection Frustration}. Time asymmetry arises directly from the interaction between the intrinsic entropic cost of state updates and the geometry of this projection. We define this using three established, parameter-free invariants of the substrate:

\begin{enumerate}
    \item \textbf{The Base Toll ($T_{geo}$):} As derived in the geometric impedance of the substrate \cite{meyer_informational_2026}, the entropic cost of a single causal state transition (the Toll pillar) is determined by the Total Node Capacity ($N = \nu_{\text{Space}} + \nu_{\text{Internal}} = 16 + 16 = 32$) and the coupling to the topological boundary:
    \begin{equation}
        T_{geo} = \frac{1}{N^3} \cdot \frac{\chi}{\sigma} \cdot \left(1 - \frac{\sigma}{D\Delta}\right) \approx 1.185 \times 10^{-5}
    \end{equation}
    \textit{Note:} The cubic dependence ($1/N^3$) was derived in \cite{meyer_informational_2026} from the minimal three-point vertex on the self-dual lattice; it manifests physically as the 3-body phase space of Weak decays.
    
    \item \textbf{The Projection Frustration ($\phi^2$):} The internal interaction space is characterized by 5-fold symmetry ($\sigma=5$), which geometrically manifests the non-crystallographic $H_4$ Coxeter group (the 600-cell). However, a fundamental theorem of crystallography dictates that 5-fold icosahedral symmetries cannot perfectly, periodically tile a 4D discrete lattice without introducing topological defects. When projecting this $H_4$ geometry onto the periodic 4-dimensional causal manifold, the eigenvalue of the projection matrix strictly defines the geometric area deficit (frustration). This eigenvalue is exactly $\phi^2 = ((1+\sqrt{5})/2)^2 \approx 2.618$, the squared Golden Ratio. This is a rigorous consequence of $H_4$ Coxeter geometry \cite{moody_quasicrystals_1993}.
    
    \item \textbf{The Coordinate Overhead ($\eta$):} Because this frustration signal is a volumetric effect that propagates through the bulk lattice before manifesting at the 4D boundary, it is subject to the Coordinate Overhead ($\eta$).
\end{enumerate}

\subsubsection{The Frustration Formula}
The Jarlskog Invariant is the fundamental causal Toll ($T_{geo}$) amplified by the Projection Frustration. The frustration acts as a geometric multiplier: every temporal state transition occurs within the constrained 4D projection, and the $\phi^2$-scaled area deficit accumulates as an additional irreducible entropic cost.

\begin{equation}
\begin{split}
    J_{geo} &= (\phi^2 \cdot \eta) \cdot T_{geo} \\
    &= (2.61803 \cdot 0.994186) \cdot \CompTOL \\
    & \approx \mathbf{\JarlskogVal}
\end{split}
\end{equation}

\subsubsection{Validation: CP Violation}

\vspace{0.5em}
\begin{tabular}{ll}
\textbf{Prediction:} & $\JarlskogVal$ \\
\textbf{Experiment:} & \JarlskogExperimentalValue \\
\textbf{Accuracy:}   & $\JarlskogSigma \sigma$ \\
\end{tabular}
\vspace{0.5em}

\subsubsection{Physical Interpretation: Projection Frustration and CP Violation}
The CP violation is a pentagonal prism casts a shadow with 5-fold symmetry onto a flat 2D surface (losing perfect symmetry in the projection), the $E_8$ lattice casts a ``Golden Shadow" onto 4D spacetime. This shadow is the Jarlskog Invariant, the geometric signature of Time's directional flow.

\begin{itemize}
    \item \textbf{Why CP violation is weak:} The geometric frustration ($\phi^2 \approx 2.6$) amplifies the Toll, but the base transition cost ($T_{geo} \approx 10^{-5}$) is inherently small due to the efficiency of the weak aperture.
    
    \item \textbf{Why matter dominates:} Without CP violation ($J=0$), the universe would be perfectly symmetric and annihilate. The non-zero $J$ creates a topological bias favoring matter over antimatter, which is subsequently amplified by cosmological expansion.
    
    \item \textbf{The Baryogenesis Gap:} While $J_{geo}$ precisely matches the Quark Sector mixing ($J_{CKM}$), this magnitude is insufficient to explain the total observed baryon asymmetry ($\eta_B \sim 10^{-9}$) through CKM physics alone. This structurally necessitates significant additional CP violation in the Lepton Sector (the PMNS matrix), which is derived in subsequent work detailing the neutrino lattice mechanism.
\end{itemize}